### 2004-07-01 Documentation/part1.tex
*** empty log message ***

\chapter{Getting started with \GLOBES }
\label{chapt:gettingstarted}

In this first chapter of the user's manual, we assume that the \GLOBES\ software is readily installed on your computer system. For the installation,
see \App~\ref{app:installation} and the {\tt INSTALL} file in the
software package. We demonstrate how to load pre-defined experiments 
and re-obtain important information about them. In addition, we discuss
some standard concepts of the \GLOBES\ user interface. We do not go
into details of the programming language, which means that standard parts
of the program code common to all examples are, in general, omitted.
An example of a minimal \GLOBES\ program in C can be found on page~\pageref{ex:c}. Furthermore, the files of the examples in this part can be found in the {\tt Example} subdirectory of your \GLOBES\ distribution. \index{Examples} Since it depends on your installed
configuration, we refer to the {\tt README} file in the \GLOBES\ main directory, and the comments in the Makefile of the {\tt Example} subdirectory for how to complile the example files.

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{llp{7cm}c}
\hline
Experiment & Filename & Short description & Refs. \\
\hline 
\multicolumn{3}{l}{\underline{Conventional beams:}} \\
??? & & \\[0.1cm]

@@

Before one can use \GLOBES , one has to initialize the \GLOBES\
library \GLB{libglobes}:
\begin{function}
\index{Initialization of {\tt libglobes}}
\index{glbInit} {\tt void glbInit(char *name)} initializes the library {\tt libglobes} and has
to be called in the beginning of each \GLOBES\ program. It takes the
name {\tt name} of the program as a string to initialize the error handling
functions. In many cases, it is sufficient to use the first
argument from the command line as the program name (such as in example on page~\pageref{ex:c}).
\end{function}

@@

For storing the experiments, \GLOBES\ uses the initially empty list of experiments \GLB{glb\_experiment\_list}. To add a pre-defined experiment to this list, one can use the function {\tt glbInitExperiment}:
\begin{function}
\index{Experiment initialization}
\index{glbInitExperiment}
{\tt int glbInitExperiment(char *inf, glb\_exp *in, int *counter)}
 adds a single experiment with the filename {\tt inf} to the list of currently loaded experiments. The {\tt counter} is a pointer to the 
 variable containg the number of experiments, and the experiment {\tt in}
 points to the beginning of the experiment list. The function returns
 zero if it was successful. 
\end{function}
Normally, a typical  call of {\tt glbInitExperiment} is 
\begin{quote}
{\tt glbInitExperiment("NuFact.glb",\&glb\_experiment\_list[0],\\  \hspace*{8cm} \&glb\_num\_of\_exps); }
\end{quote}
In this case, the experiment in the file {\tt NuFact.glb} is added to the internal global list of experiments, and the experiment counter is increased. The
experiment then has the number {\tt glb\_num\_of\_exps}-1. The elements
of the experiment list have the type \GLB{glb\_exp}, which the
user will not need to access directly in most cases. The experiment definition files, which usually end with {\tt .glb}, and any
supporting files, are first of all searched in the current directory, and then in the global path variable \GLB{GLB\_PATH} set in your environment.
A list of pre-defined experiment prototypes, their filenames, their short descriptions, and the references of their definitions can be found in \tabl{experiments}. If the program cannot find these files, or some of them are syntactially not correct, it will break at this place.

One can also remove all experiments from the evaluation list at running
 time:
\begin{function}
\index{glbClearExperimentList}
{\tt void ClearExperimentList()} removes all experiments from the internal list and resets all counters.   
\end{function}
Note that changing the number of experiments requires a new initialization
of all parameters of the types \GLB{glb\_params} and \GLB{glb\_projection}
if the number of experiments changes, since these parameter structures internally carry lists for the matter densities of all experiments. Similarly, once should never call {\tt glbAlloc...} before the
experiment initialization.

\begin{table}[t]
\begin{center}
\begin{tabular}{llp{7cm}}
\hline
Quantities & Examples & Units \\
\hline
Angles & $\theta_{13}$, $\theta_{12}$, $\theta_{23}$, $\deltacp$ & Radians  \\
Mass squared differences & $\sdm$, $\ldm$ & $\mathrm{eV}^2$ \\
Matter densitities & $\rho_i$ & $\mathrm{g}/\mathrm{cm}^3$ \\
Baseline lengths & $L_i$ & $\mathrm{km}$ \\
Energies & $E_\nu$ & $\mathrm{GeV}$ \\  
Fiducial masses & $m_{\mathrm{Det}}$ & $\mathrm{t}$ (reactor exp.) or $\mathrm{kt}$ (accelerator exp.), \newline  depends on experiment definition \\
Time intervals & $t_{\mathrm{run}}$ & $\mathrm{yr}$ \\
Source powers & $P_{\mathrm{Source}}$ & Useful parent particle decays/$\mathrm{yr}$ \newline (Neutrino factory, $\beta$-Beam), \newline $\mathrm{GW}$ thermal power (reactor exps.), \newline or
$\mathrm{MW}$ target power (superbeams); \newline
depends on flux definition
 \\
% Integrated luminosities & $m_{\mathrm{Det}} \, t_{\mathrm{run}}$ & $\mathrm{kt \cdot yr}$ \\
Cross sections/E & $\sigma_{\mathrm{CC}}/E$ & $10^{-38} \, \mathrm{cm^2}/\mathrm{GeV^2}$ \\
\hline
\end{tabular}
\mycaption{\label{tab:units} \index{Units in \GLOBES } Quantities used in \GLOBES , examples of these quantities, and their standard units in the application software.}
\end{center}
\end{table}

While interacting with the user interface of \GLOBES , parameters are transferred to and from the \GLOBES\ library. In \GLOBES , one set of units 
for each type of quantity is used in order to avoid confusion about the definition of individual parameters. \tabl{units} summarizes the units of the most important quantities. In principle, the event rates are
proportional to the product of source power $\times$ target mass $\times$
 running time, which we call ``integrated luminosity''. Since especially the
 definition of the source power depends on the experiment type, the quantities of the three luminosity components
 are not unique and depend on the experiment definition. Usually,
 one uses detector masses in kilotons for beam experiments,
 and detector masses in tons for reactor experiments. Running times
 are normally given in years, where it is often assumed that the 
 experiment runs $100\%$ of the year. Thus, for shorter running periods,
 the running times need to be renormalized. Source powers are
 usually useful parent particle decays per year (neutrino factories,
 $\beta$-beams), target power in megawatts (superbeams), or thermal
 reactor power in gigawatts (reactor experiments).

WW: WEITER FROM HERE:

Since the pre-defined experiments in \tabl{experiments} are given for one year running time, specific target masses, and specific source powers, it is useful to change these parameters of the individual experiments:
\begin{function}
\GLB{SetRunningTime}$(N_{\mathrm{exp}},t_{\mathrm{run}})$ sets the running time of experiment number $N_{\mathrm{exp}}$ to $t_{\mathrm{run}}$ years.
\end{function}
 \begin{function}
\GLB{SetTargetMass}$(N_{\mathrm{exp}},m_{\mathrm{Det}})$ sets the fiducial mass of experiment number $N_{\mathrm{exp}}$ to $m_{\mathrm{Det}}$ kilotons.
\end{function}
\begin{function}
\GLB{SetSourcePower}$(N_{\mathrm{exp}},P_{\mathrm{Source}})$ sets the source power of experiment number $N_{\mathrm{exp}}$ to $P_{\mathrm{source}}$. The definition of the source power depends on the experiment type: ... (MISSING).
\end{function}
Thus, these functions also demonstrate how to use the assigned experiment number.

A useful function to re-obtain the information about the initialized experiments is the function {\tt InfoExperiment}:
\begin{function}
\GLB{InfoExperiment}$()$ prints a list of the initialized functions with their experiment numbers and their most important parameters to the standard output.
\end{function} 
Especially, after changing individual parameters, such as baseline or target mass, this information can be useful to check the changes. Another useful function is {\tt ShowChannels}, which prints the initialized oscillation channels for a specified experiment:
\begin{function}
\GLB{ShowChannels}$(N_{\mathrm{exp}})$ prints the information about the oscillation channels of the experiment with the number $N_{\mathrm{exp}}$ to the standard output.
\end{function}

Compared to an existing experiment, which uses real data, a future experiment uses simulated data. Thus, the {\em true parameter values} and their results in form of the reference rate vectors are simulated. After setting the true parameter values, the {\em fit parameter values} can be varied in order to obtain information on the measurement performance for the given set of true parameter values. Therefore, it is often useful to show the results of a future measurement as function of the true parameter values for which the reference rate vectors are computed -- at least within the currently allowed ranges. The true parameter values for the vacuum neutrino oscillation parameters have to be set by the functions {\tt SetVacuumParameters} and {\tt SetRates} {\em before} any evaluation function is used and {\em after} the experiments have been initialized and the experiment parameters have been adjusted which could change the rates (such as baseline or target mass). Any matter effects are then included automatically depending on the experiment definitions.
\begin{function}
\GLB{SetVacuumParameters}$(\{\theta_{12}, \theta_{13}, \theta_{23}, \deltacp , \sdm , \ldm \})$ sets the neutrino oscillation parameters to be used to compute the reference rate vector in vacuum.
\end{function}
\begin{function}
\GLB{SetRates}$( )$ computes the reference rate vector for the neutrino oscillation parameters set with {\tt SetVacuumParameters}. 
\end{function}
Finally, an initialization sequence for \GLOBES\ could look like this:
\begin{quote}
{\tt
ClearExp(); \\
InitExperiment("JHFHK.exp"); \\
SetRunningTime(0, 2.0); \\
InitExperiment("JHFHKanti.exp"); \\
SetRunningTime(1, 6.0);\\
MInfoExperiment(); \\
SetVacuumParameters(\{0.55, 0.16, 3.14/4, 3.14/2, 7e-5, 2e-3\}); \\
SetRates();
} 
\end{quote}
This piece of code initializes the JHF (J-PARC) to Hyper-Kamiokande superbeam upgrade with two years of neutrino running and six years of antineutrino running, \ie, an overall running time of eight years. The final configuration is then printed to the standard output and the reference rate vector is set to the chosen parameter values.

>>>>

\chapter{\GLOBES\ basics}
\label{chapt:gettingstarted}

In this first chapter of the user's manual, we assume that the \GLOBES\ software is readily installed on your computer system. For the installation,
see \App~\ref{app:installation} and the {\tt INSTALL} file in the
software package. We demonstrate how to load pre-defined experiments 
and introduce the basic concepts of \GLOBES . We do not go
into details of the programming language, which means that standard parts
of the program code common to all of the examples in the following chapters are, in general, omitted.
An example of a minimal \GLOBES\ program in C can be found on page~\pageref{ex:c}. Furthermore, the files of the examples in this part can be found in the {\tt Example} subdirectory of your \GLOBES\ distribution. \index{Examples} Since it depends on your installed
configuration, we refer to the {\tt README} file in the \GLOBES\ main directory, and the comments in the Makefile of the {\tt Example} subdirectory for how to complile the example files.

@@

\begin{table}[tbp]
\begin{center}
\begin{tabular}{llp{7cm}c}
\hline
Experiment & Filename & Short description & Refs. \\
\hline 
\multicolumn{3}{l}{\underline{Conventional beams:}} \\
??? & & \\[0.1cm]

@@

Before one can use \GLOBES , one has to initialize the \GLOBES\
library \GLB{libglobes}:
\begin{function}
\index{Initialization of {\tt libglobes}}
\GLBNS{glbInit} {\tt void glbInit(char *name)} initializes the library {\tt libglobes} and has
to be called in the beginning of each \GLOBES\ program. It takes the
name {\tt name} of the program as a string to initialize the error handling
functions. In many cases, it is sufficient to use the first
argument from the command line as the program name (such as in example on page~\pageref{ex:c}).
\end{function}

@@

For storing the experiments, \GLOBES\ uses the initially empty list of experiments \GLB{glb\_experiment\_list}. To add a pre-defined experiment to this list, one can use the function {\tt glbInitExperiment}:
\begin{function}
\index{Experiment initialization}
\GLBNS{glbInitExperiment}
{\tt int glbInitExperiment(char *inf, glb\_exp *in, int *counter)}
 adds a single experiment with the filename {\tt inf} to the list of currently loaded experiments. The {\tt counter} is a pointer to the 
 variable containg the number of experiments, and the experiment {\tt in}
 points to the beginning of the experiment list. The function returns
 zero if it was successful. 
\end{function}
Normally, a typical  call of {\tt glbInitExperiment} is 
\begin{quote}
{\tt glbInitExperiment("NuFact.glb",\&glb\_experiment\_list[0],\\  \hspace*{8cm} \&glb\_num\_of\_exps); }
\end{quote}
In this case, the experiment in the file {\tt NuFact.glb} is added to the internal global list of experiments, and the experiment counter is increased. The
experiment then has the number {\tt glb\_num\_of\_exps}-1. The elements
of the experiment list have the type \GLB{glb\_exp}, which the
user will not need to access directly in most cases. The experiment definition files, which usually end with {\tt .glb}, and any
supporting files, are first of all searched in the current directory, and then in the global path variable \GLB{GLB\_PATH} set in your environment.
A list of pre-defined experiment prototypes, their filenames, their short descriptions, and the references of their definitions can be found in \tabl{experiments}. If the program cannot find these files, or some of them are syntactially not correct, it will break at this place.

One can also remove all experiments from the evaluation list at running
 time:
\begin{function}
\GLBNS{glbClearExperimentList}
{\tt void glbClearExperimentList()} removes all experiments from the internal list and resets all counters.   
\end{function}
Note that changing the number of experiments requires a new initialization
of all parameters of the types \GLB{glb\_params} and \GLB{glb\_projection}
if the number of experiments changes, since these parameter structures internally carry lists for the matter densities of all experiments. Similarly, once should never call {\tt glbAlloc...} before the
experiment initialization.

\begin{table}[tb]
\begin{center}
\begin{tabular}{llp{7cm}}
\hline
Quantities & Examples & Units \\
\hline
Angles & $\theta_{13}$, $\theta_{12}$, $\theta_{23}$, $\deltacp$ & Radians  \\
Mass squared differences & $\sdm$, $\ldm$ & $\mathrm{eV}^2$ \\
Matter densitities & $\rho_i$ & $\mathrm{g}/\mathrm{cm}^3$ \\
Baseline lengths & $L_i$ & $\mathrm{km}$ \\
Energies & $E_\nu$ & $\mathrm{GeV}$ \\  
Fiducial masses & $m_{\mathrm{Det}}$ & $\mathrm{t}$ (reactor exp.) or $\mathrm{kt}$ (accelerator exp.), \newline  depends on experiment definition \\
Time intervals & $t_{\mathrm{run}}$ & $\mathrm{yr}$ \\
Source powers & $P_{\mathrm{Source}}$ & Useful parent particle decays/$\mathrm{yr}$ \newline (Neutrino factory, $\beta$-Beam), \newline $\mathrm{GW}$ thermal power (reactor exps.), \newline or
$\mathrm{MW}$ target power (superbeams); \newline
depends on flux definition
 \\
% Integrated luminosities & $m_{\mathrm{Det}} \, t_{\mathrm{run}}$ & $\mathrm{kt \cdot yr}$ \\
Cross sections/E & $\sigma_{\mathrm{CC}}/E$ & $10^{-38} \, \mathrm{cm^2}/\mathrm{GeV^2}$ \\
\hline
\end{tabular}
\mycaption{\label{tab:units} \index{Units in \GLOBES } Quantities used in \GLOBES , examples of these quantities, and their standard units in the application software.}
\end{center}
\end{table}

While interacting with the user interface of \GLOBES , parameters are transferred to and from the \GLOBES\ library. In \GLOBES , one set of units 
for each type of quantity is used in order to avoid confusion about the definition of individual parameters. \tabl{units} summarizes the units of the most important quantities. In principle, the event rates are
proportional to the product of source power $\times$ target mass $\times$
 running time, which we call ``integrated luminosity''. Since especially the
 definition of the source power depends on the experiment type, the quantities of the three luminosity components
 are not unique and depend on the experiment definition. Usually,
 one uses detector masses in kilotons for beam experiments,
 and detector masses in tons for reactor experiments. Running times
 are normally given in years, where it is often assumed that the 
 experiment runs $100\%$ of the year. Thus, for shorter running periods,
 the running times need to be renormalized. Source powers are
 usually useful parent particle decays per year (neutrino factories,
 $\beta$-beams), target power in megawatts (superbeams), or thermal
 reactor power in gigawatts (reactor experiments).
%
Since the pre-defined experiments in \tabl{experiments} are given for specfific luminosities, it is useful to change these parameters of the
individual experiments:
\begin{function}
\GLBNS{glbSetSourcePower}
{\tt void glbSetSourcePower(double power, int exp, int fluxno)}
 sets the source power of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt power}. The definition of the source power depends on the experiment type as described above.
\end{function}
\begin{function}
\GLBNS{glbSetRunningTime}
{\tt void glbSetRunningTime(double time, int exp, int fluxno)}
 sets the running time of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt time} years.
\end{function}
\begin{function}
 \GLBNS{glbSetTargetMass}
{\tt void glbSetTargetMass(double mass,int exp)}
sets the fiducial detector mass of experiment number {\tt exp} to {\tt mass} tons or kilotons (depending on the experiment definition).
\end{function}
Thus, these functions also demonstrate how to use the assigned experiment number and others. These numbers run from $0$ to the number of experiments-1, fluxes-1, \etc, where the individual elements are numbered in the order of their appearance. 
 Note that the source power and running time are quantities defined
together with the neutrino flux, whereas the target mass scales the whole
experiment.

Before we can set the simulated event rates or access any oscillation
parameters, we need to become familiar with the concept \GLOBES\ uses
for oscillation parameters. In order to transfer sets of oscillation
parameter vectors $(\theta_{12}, \theta_{13}, \theta_{23}, \deltacp, \sdm, \ldm)$, the parameter type \GLB{glb\_params\_type} is used. In general, pointers to this structure are of the type \GLB{glb\_params}, and are often
transferred to and from \GLOBES\ functions. Therefore, the memory space
for these vectors has to be reserved before they can be used, and it has
to be returned afterwards. \GLOBES\ functions usually use the pointers
of the type {\tt glb\_params} for the input or output to the functions. As
an input parameter, the pointer has to be created and point towards a valid
parameter structure, where the oscillation parameters are read from. As
an output parameter, the pointer has to be created, too, and point towards
a structure which will contain the return values will be written to.
This parameter transfer concept seems to be very sophisticated, but, as we
will see in the next chapters, it hides a lot of complicated parameter 
mappings which otherwise need to be done by the user. For example, not
only the oscillation parameters are stored in the pointer structure, but also information on the
densities of all of the initialized experiments. Since \GLOBES\ treats
the matter density as a free parameter known with some external precision
to include matter density uncertainties,
the minimizers also use fit values and external errors for the matter
densities of all loaded experiments. More precisely, the matter density
profile of each experiment $i$ is multiplied by a scaling factor
$\hat{\rho_i}$, \index{Density scaling factor} 
which is stored in the density information of {\tt glb\_params}. Each of
these scaling factors has $1.0$ as pre-defined value. Since it
is in most cases not necessary to change this value, the user does
not need to take care of these values.\footnote{For more information,
we refer to the following chapters.}
Note that the {\tt glb\_params}
structures must not be initialized before all experiments are loaded,
since the number of matter densities can only be determined after the
experiments are initialized. 
Similarly, any change in the number of experiments requires that the
parameter structures be re-initialized, \ie, destroyed and created again.
Another piece of information returned from the minimizers and transferred
into the {\tt glb\_params} structure is the number
of iterations used for the minimization, which is proportional to the
running time of the minimizer. In general, the user does not need to
access the elements in {\tt glb\_params} directly. A number of functions
is provided to handle these parameter structures:
\GLBNS{glbAllocParams}
{\tt glb\_params glbAllocParams()} allocates the memory space
needed for a parameter vector and returns a pointer to it.
\GLBNS{glbAllocParams}
{\tt void glbFreeParams(glb\_params stale)} destroys the memory space
needed for a parameter vector {\tt stale} and sets the pointer to {\tt NULL}.
\GLBNS{glbDefineParams}
{\tt glb\_params glbDefineParams(glb\_params in, double theta12, double theta13,double theta23, double delta, double dms, double dma)} assigns
the complete set of oscillation parameters to the vector {\tt in}, which has
to be allocated before. The return value is the pointer to {\tt in} if 
the assignment was successful, and {\tt NULL} otherwise.
 \GLBNS{glbCopyParams}
 {\tt glb\_params glbCopyParams(const glb\_params source, glb\_params dest)}
 copies the vector {\tt source} to the vector {\tt destination}. The return
 value is {\tt NULL} if the assignment was not successful.
\GLBNS{glbPrintParams}
{\tt void glbPrintParams(FILE *stream, const glb\_params in)} prints the
parameters in {\tt in} to the file {\tt stream}. The oscillation
parameters, all density values, and the number of iterations are
printed as pretty output.
In addition to these basic functions, there are functions to access
the individual parameters within the parameter vectors:
\GLBNS{glbSetOscParams}
{\tt glb\_params glbSetOscParams(glb\_params in, double osc, int which)}
sets the oscillation parameter {\tt which} in the structure {\tt in}
to the value {\tt osc}. If the assignment was unsuccessful, the 
function returns {\tt NULL}.
\GLBNS{glbGetOscParams}
{\tt double glbGetOscParams(glb\_params in, int which)}
returns the value of the oscillation parameter {\tt which} in the 
structure {\tt in}.
In both of these functions, the parameter {\tt which} runs from
$0$ to $5$, where the parameters in \GLOBES\ always have the order $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\deltacp$, $\sdm$, $\ldm$.
Alternatively to the number, the constants \GLB{GLB\_THETA\_12}, \GLB{GLB\_THETA\_13}, \GLB{GLB\_THETA\_23}, \GLB{GLB\_DELTA\_CP}, 
\GLB{GLB\_DM\_SOL}, or \GLB{GLB\_DM\_ATM} can be used.

Similarly, the density parameters or iterations can be accessed:
\begin{function}
\GLBNS{glbSetDensityParams}
{\tt glb\_params glbSetDensityParams(glb\_params in, double dens, int which)} sets the density parameter {\tt which} in the structure {\tt in}
to the value {\tt dens}. If the assignment was unsuccessful, the 
function returns {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{glbGetDensityParams}
{\tt double glbGetDensityParams(glb\_params in, int which)}
returns the value of the density parameter {\tt which} in the 
structure {\tt in}.
\end{function}
\begin{function}
\GLBNS{glbSetIteration}
{\tt glb\_params glbSetIteration(glb\_params in, int iter)} sets the number of iterations in the structure {\tt in}
to the value {\tt iter}. If the assignment was unsuccessful, the 
function returns {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{glbGetIteration}
{\tt int glbGetIteration(glb\_params in)}
returns the value of the number of iterations in the 
structure {\tt in}.
\end{function}
In total, the parameter vector handling in a program normally has the
following order:
\begin{quote}
{\tt
glbInitExperiment(...); \\
/* ... more initializations ... */ \\
\\
glb\_params vector1 = glbAllocParams(); \\
/* ... more vectors allocated ... */ \\
\\
/* Program code: assign and use vectors */ \\
\\
glbFreeParams(vector1); \\
/* ... more vectors destroyed ... */ \\
\\
/* ... end of program or glbClearExperimentList ... */ 
}
\end{quote}
Compared to existing experiments, which use real data, future experiments
uses simulated data. Thus, the {\em true parameter values} and their results in form of the reference event rate vectors are simulated. After setting the true parameter values, the {\em fit parameter values} can be varied in order to obtain information on the measurement performance for the given set of true parameter values. Therefore, it is often useful to show the results of a future measurement as function of the true parameter values for which the reference rate vectors are computed -- at least within the currently allowed ranges. The true parameter values for the vacuum neutrino oscillation parameters have to be set by the functions \GLB{glbSetOscillationParameters} and \GLB{glbSetRates} {\em before} any evaluation function is used and {\em after} the experiments have been initialized and the experiment parameters have been adjusted which could change the rates (such as baseline or target mass). This means that
after any change of an experiment parameter, {\tt glbSetRates} has to be called. Matter effects are automatically included as specified in the experiment definition. We have the following functions to assign and
read out the vacuum oscillation parameters:
\begin{function}
\GLBNS{glbSetOscillationParameters}
{\tt int glbSetOscillationParameters(const glb\_params in)} sets the
vacuum oscillation parameters to the ones in the vector {\tt in}.
\end{function}
\begin{function}
\GLBNS{glbGetOscillationParameters}
{\tt int glbGetOscillationParameters(glb\_params out)} returns the
vacuum oscillation parameters in the vector {\tt out}. The result of
the function is $0$ if the call was successful.
\end{function}
The reference rate vector is then computed with:
\begin{function}
\GLBNS{glbSetRates}
{\tt void glbSetRates()} computes the reference rate vector for the neutrino oscillation parameters set by {\tt glbSetOscillationParameters}. 
\end{function}
A complete example for a minimal \GLOBES\ program can be found on
Page~\pageref{ex:c}.
